### 2022-03-22 ms/PrestigeBias.tex
update

\subsection{Prestige in medicine \citep{medical_prestige}}
So far we presented the existence of prestige in nature and in humans. We mostly discussed it in regard of social ranking in animals, and what are the costs and benefits. In humans, we mostly addressed spread of adaptive or maladaptive traits due to the prestige bias. \citet{medical_prestige} present a specific and important effect of prestige - its significance for medical specialties and diseases.
They examined literature from 1950 to 2005 regarding the effects of prestige on medicinal practices. They discovered that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, while medicine with opposite characteristics had low levels of prestige. They have concluded that such differences in prestige bear consequences for actual priority setting in healthcare systems. They discovered that surgery counts as the most prestigious specialty, while psychiatry is the less prestigious. In addition, doctors tend to rank practices that require more time to master as more prestigious, while other procedures that are considered \textit{easier} are less prestigious. \citet{medical_prestige} found that the advance in technology and research was in accordance with the prestige rankings.
\clearpage
\bibliography{refs}
\bibliographystyle{apalike}
\end{document}

>>>>

\subsection{Prestige in medicine \citep{medical_prestige}}
So far we presented the existence of prestige in nature and in humans. We mostly discussed it in regard of social ranking in animals, and what are the costs and benefits. In humans, we mostly addressed spread of adaptive or maladaptive traits due to the prestige bias. \citet{medical_prestige} present a specific and important effect of prestige - its significance for medical specialties and diseases.
They examined literature from 1950 to 2005 regarding the effects of prestige on medicinal practices. They discovered that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, while medicine with opposite characteristics had low levels of prestige. They have concluded that such differences in prestige bear consequences for actual priority setting in healthcare systems. They discovered that surgery counts as the most prestigious specialty, while psychiatry is the less prestigious. In addition, doctors tend to rank practices that require more time to master as more prestigious, while other procedures that are considered \textit{easier} are less prestigious. \citet{medical_prestige} found that the advance in technology and research was in accordance with the prestige rankings.

\subsection{Collective brains \citep{collective_brains}}
We showed cultural transmission is a process that manifests in many species, with emphasis on humans. We also displayed similarities between this process and genetic transmission, while presenting differences between them, specifically selective biases such as influence and prestige. \citet{collective_brains} offer a take on prestige as a factor of human physical evolution. They present a concept called \textit{cultural brains} - brains that evolved primarily for the acquisition of adaptive knowledge.
They build on the hypothesis of \citet{social_brains} that shows that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
\citet{collective_brains} built a model that predicts a strong relationship between brain size and group size, because group size also provides access to more adaptive knowledge. They later present their \textit{cumulative cultural brain} hypothesis, an approach which proposes that human brains have evolved with an ability and proclivity for selective, high fidelity social learning. As part of this process, there are a variety of strategies and biases that have evolved to hone in on the most adaptive knowledge. These strategies and biases include direct and indirect cues of the popularity of cultural traits (e.g. success and prestige biases).
In short, they suggest that some of the reasons for the extreme increase in brain size in humans, are the ability to "cheaply" acquire adaptive knowledge, i.e transmission biases, such as prestige.

\subsection{Prestige-biased cultural learning \citep{prestige_cultural_learning}}
Culture–gene coevolutionary (CGC) researchers theorize that humans should possess several learning biases which robustly enhance the fitness of cultural learners. 
\citet{prestige_cultural_learning} report the first direct tests in children of CGC's prediction of \textit{prestige bias}, a tendency to learn from individuals to whom others have preferentially attended, learned or deferred.
Their definition of prestige is similar to our \textit{influence bias}, and brings concrete proof of its existence and effects. Their study showed that the odds of 3-4 years-old children learning from an adult model to whom bystanders had previously preferentially attended for 10 seconds were over twice those of their learning from a model whom bystanders ignored.
In addition to this first study, they also discovered prestige effects are domain-sensitive. They saw that prestigious models were listened to by most when demonstrating artifact-use, but not as much as when presenting food preferences. It lead \citet{prestige_cultural_learning} to believe that when the trait is costly to learn individually, prestige will have a higher effect. It would be interesting to include costs in our model to try and observe these effects and their dynamics in the simulations of a larger population than this study.

\clearpage
\bibliography{refs}
\bibliographystyle{apalike}
\end{document}
